### 2023-09-11 chapters/paper_modelagnostic.tex
Fix typo

Another line of works blame the models themselves and not the test statistics. \textcite{zhang_understanding_2021} argued that model misestimation is the main cause of higher likelihood assigned to OOD data. This can be due to both the model architecture and the maximum likelihood objective. \textcite{kirichenko_why_2020} and \textcite{schirrmeister_understanding_2020} showed that normalizing flows can achieve better OOD performance despite achieving a worse likelihood if one changes some model design choices.
%
Other works in the literature focused on deriving specific test statistics that works only for a specific model, for example for VAEs \parencite{xiao_likelihood_2020, maaloe_biva_2019, havtorn_hierarchical_2021}, or for normalizing flows \parencite{kirichenko_why_2020, ahmadian_likelihoodfree_2021}.

>>>>

Another line of works blame the models themselves and not the test statistics. \textcite{zhang_understanding_2021} argued that model misestimation is the main cause of higher likelihood assigned to OOD data. This can be due to both the model architecture and the maximum likelihood objective. \textcite{kirichenko_why_2020} and \textcite{schirrmeister_understanding_2020} showed that normalizing flows can achieve better OOD performance despite achieving a worse likelihood if one changes some model design choices.
%
Other works in the literature focused on deriving specific test statistics that work only for a specific model, for example for VAEs \parencite{xiao_likelihood_2020, maaloe_biva_2019, havtorn_hierarchical_2021}, or for normalizing flows \parencite{kirichenko_why_2020, ahmadian_likelihoodfree_2021}.
